### 2014-11-13 tex/abstract.tex
some minor tweaks to the abstract

A fundamental challenge of using symbolic execution for software
analysis has been the treatment of dynamically allocated
data. Generalized symbolic execution (GSE) techniques have addressed
this challenge by materializing a concrete heap lazily during field
accesses.  This approach however, exacerbates the state space
explosion problem.  In this work, we present a novel symbolic
execution technique which takes inspiration from the static analysis
domain and defines a novel bipartite graph representation of the heap
and a lazy initialization algorithm that, unlike state-of-the-art
techniques, (a) supports aliasing, (b) does not require rewrite of
constraints on heap updates, (c) can initialize the heap-on-the-fly,
and (d) reduces the number of points of non-determinism during the
search. Our approach is sound and complete with respect to the
properties provable by GSE. A preliminary evaluation of our
implementation in Java Pathfinder shows the summary heap enables the
initialization of larger more complex heaps than previously possible.

>>>>

A fundamental challenge of using symbolic execution for software
analysis has been the treatment of dynamically allocated
data. Generalized symbolic execution (GSE) techniques have addressed
this challenge by materializing a concrete heap lazily during field
accesses.  These techniques however, exacerbate the path explosion
problem.  In this work, we present a heap summary approach which takes
inspiration from the static analysis domain and defines a bipartiate
graph to encode multiple heaps in single representation, which, unlike
state-of-the-art static analysis approaches, (i) supports aliasing,
(ii) does not require rewrite of constraints on heap updates, and
(iii) can initialize the heap-on-the-fly. We also define a heap
summary algorithm to perform heap updates during symbolic execution on
this representation in order to mitigate the path explosion problem in
GSE techniques. Our approach is sound and complete with respect to the
properties provable by GSE. A preliminary evaluation of our
implementation in Java Pathfinder framework shows the summary heap
enables the initialization of larger, more complex heaps than
previously possible.
